---
title: "p8105_hw6_as5685"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mgcv)
library(modelr)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```


### Load in data
```{r, message=FALSE}
child_growth = read_csv("./data/birthweight.csv")
skimr::skim(child_growth)
```
* no missing

### Tidy data

```{r, message=FALSE}
child_growth_clean = 
child_growth %>% 
  mutate(
    babysex = recode_factor(babysex, `1` = "male", `2` = "female"),
    frace = recode_factor(frace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown"),
    mrace = recode_factor(mrace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other"),
    malform = recode_factor(malform, `0` = "absent", `1` = "present"),
    bwt = bwt * 0.0022
  )
```

* There is no missing data in the dataset. Categorical variables were transfered to factor from numeric. 

### Building My own model

```{r}
child_growth_clean = 
  child_growth_clean %>% 
  mutate(
    babysex = fct_infreq(babysex)
  )
mymodel = lm(bwt ~ babysex+blength + delwt + fincome + gaweeks, data = child_growth_clean)

mymodel %>% 
  broom::glance() %>% view

mymodel %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

plots = 
child_growth_clean %>% 
  modelr::add_residuals(mymodel) %>% 
  modelr::add_predictions(mymodel) %>% 
  ggplot(aes(x = pred, y =  resid)) + geom_point() + 
  labs(
    x = "prediction",
    y = "residuals",
    title =  "prediction and residuals"
  )
plots

```

* I chose the potential factors that underly birthweight: `babysex`, `blength`, `delwt`, `fincome`, `gaweeks`. baby sex and baby's length will direcly influence the weight of newborns. family income will affect the mother's health condition, thereby cause the difference on newborns' weights. Also, less gastational age will lead to higher possibilities to lighter babies. 



### Comparison

```{r, message=FALSE}
cv_df = 
  crossv_mc(child_growth_clean, 100)

cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_df = 
  cv_df %>% 
  mutate(
    mymodel = map(train, ~lm(bwt ~ babysex + blength + delwt + fincome + gaweeks, data = .x)),
    maineffect = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    threewayinteraction = map(train,~lm(bwt ~ bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmse_mymodel = map2_dbl(mymodel, test, ~rmse(model = .x, data = .y)),
    rmse_maineffect = map2_dbl(maineffect, test, ~rmse(model = .x, data = .y)),
    rmse_threewayinteraction = map2_dbl(threewayinteraction, test, ~rmse(model = .x, data = .y))
    )

comparison_plot =
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse", 
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() +
  labs(
    title = "model comparison"
  )

comparison_plot


```

## Question 2

### load in data
```{r, message=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


## clean 
```{r}
weather_df_clean =
weather_df %>% 
  select(tmax, tmin)

```


## drawing the plot
```{r}
r_df =
  weather_df_clean %>% 
  modelr::bootstrap(5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin , data = .x)),
    results = map(models, broom::glance)) %>% 
  unnest(results)

plot_r = 
  r_df %>%   
  ggplot(aes(x = r.squared)) + geom_density() + 
  labs(
    title = "Distribution of r.squared"
  )

plot_r
  

log_df =
  weather_df_clean %>% 
  modelr::bootstrap(5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin , data = .x)),
    results = map(models, broom::tidy)) %>% 
  unnest(results) %>% 
  select(.id, estimate, term) %>% 
  pivot_wider(
  names_from = "term",
  values_from = "estimate"
    ) %>% 
  mutate(
    log = log(`(Intercept)`*tmin)
  ) 

plot_log = 
   log_df %>% 
    ggplot(aes(x = log)) + geom_density() +
    labs(
      title = "Distribution of log(intercept*beta1)"
    )
plot_log


quantile(log_df$log, probs = c(0.025, 0.975))
quantile(r_df$r.squared, probs = c(0.025, 0.975))

```

* Two plots mostly have normal distribution. The 95% CI for log(intercept*beta1) is `r quantile(log_df$log, probs = c(0.025, 0.975))`. The 95% CI for r.squared is `r quantile(r_df$r.squared, probs = c(0.025, 0.975))`. 


















